Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-07-13 manuscript/bef_stability/manuscript.Rmd
Review discussion

Our aim was to evaluate the effects of the network structure on the total
biomass and its temporal stability in natural communities, which have been
poorly documented. To do so, we quantified the effects, directs and indirects,
of habitat properties, species richness, and food web structure, on the biomass
and stability of fish communities, from the ONEMA fish dataset, containing over
X million individual fish samples, across 99 locations France spanning the
period 1995 to 2018.  We infered trophic interactions networks based on body
size-dependency in food diet from the literature and prey/predator body size
ratio for piscivory^[ We inferred trophic networks at the scale of trophic
species (i.e. nodes being body size classes) to take in account ontogenic diet
shifts and that fish-fish trophic interaction depends on body size ratio between
prey and predator. On the other side, the community metrics were defined at the
species level, (i.e.  species richness, average species CV and synchrony).  ].
We built structural equation models to disantangle the direct and indirect
effects of environmental drivers, species richness and network structure on both
total biomass and biomass stability.  We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively.  Futhermore, we found that the effect of species richness
and mean trophic level on total biomass and its temporal stability were not
independant as species richness had a positive effect on mean trophic level.
Finally, we found that the magnitude of the effects of average temperature and
altitude was equal or superior to the effects of species richness and mean
trophic level. Overall, our study is unique by its level of integration, from
environmental effects to total biomass and stability, going through species
richness and network structure, and the first direct assessment of a possible
joint effect of species richness and network structure.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
richness on total biomass might be due to resource use complementarity, which is
held by niche differentiation and interspecific facilitation
[@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
or might be due to positive select effect which takes place through the
dominance of the most productive species [@tilman_plant_1997;
@loreau_partitioning_2001]. Previous research seems to indicate that resource
complementarity might be the main driver in fish communities
[@carey_determining_2011] but futher invesgations are needed to assess the
dominance of this mecanism in aquatic communities and more generally in food
webs.

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in
grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
and even in natural communities [@olivier_independent_nodate] where positive
relationships are typically found between temporal stability and species
richness. In streams as well, @franssen_annual_2011 found that species richness
increased temporal stability. However other studies found a opposite relationship
in natural grassland [@yang_effects_2011] or a marginal one
[@declerck_species_2006] in natural forests. Further investigations are needed
to identify the mechanisms behind those contrasting patterns. A first step is 
be to look at the effects of species richness on synchrony and
$\overline{CV_{sp}}$, which constitute the two components of temporal stability
quantified as CV [@loreau_species_2008; @thibaut_understanding_2013].

We found that species richness decreases synchrony, thereby increasing
stability. Species richness can reduce synchrony through decrease of population
size, thus raising the role of demographic stochasticity [@loreau_species_2008]
but also in the case where species have different responses to environmental
variation [@loreau_species_2008]. While
a negative effect of species richness on synchrony is generally found in
experimental grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011],
no relation has been found in natural forests [@declerck_species_2006], but
negative relationships have been found in natural communities of birds, bats,
grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_independent_nodate]. Our study thus highlights that species richness
might also decrease synchrony in empirical trophic communities.

Whereas the positive effect of species richness on $\overline{CV_{sp}}$, thereby
decreasing stability, was more intriguing. Indeed, precedent studies found that
constrasting results. For example, @olivier_independent_nodate reported negative, neutral and
positive effect of species richness on $\overline{CV_{sp}}$ in respectively
butterfly, bat and birds communities. @thibaut_understanding_2013 proposed that
two ingredients can generate a positive effect of species richness on
population ($\overline{CV_{sp}}$) stability: a strongly uneven biomass
distribution across populationand that the biomass variance
of population increases much faster than its mean.

In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013]. However, it was unexpected that the average
population $\overline{CV_{sp}}$ had a stronger negative effect on biomass
stability than synchrony [@bluthgen_land_2016; @olivier_independent_nodate]. We
can advance two hypothesis that can raise this effect. First, the opportunity
for diet differentiation can be low in streams compare to other organisms.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

@@

The mean trophic level was positively linked to total biomass. This result is
straightforward. As feeding interactions were partly determined by body size and
that body mass increase with body size, it is expected that the more the average
biomass is located at higher trophic level, the more the total biomass
increase. A mechanism, suggested by experimental and theoretical work, can
be that a higher trophic level is the result of a stronger top-down effect,
meaning higher predation rates and biomass fluxes to higher trophic levels
[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
increase in total biomass with vertical diversity. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increases
with the length of trophic chain and so results in higher total biomass. 
In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance should translate in higher resource transfer
efficiency between prey and predators and so results in higher total biomass in
the fish compartment. A reason for such an absence of an effect might be the
little resolution that we have about interactions in non fish compartment (Fig.
\@ref(fig:methods) C, D). A consequence can be that our connectance measurement
contains few too informations.

mean trophic level had a positive effect on biomass stability by its negative
effect on CVsp (i.e. positive effect on average species stability). It means
that species at higher trophic level are more stable than the species at lower
trophic levels. @shanafelt_stability_nodate and @barbier_pyramids_2019
found the same pattern with pure trophic chain models. They have shown that
strong top-down control can generate this pattern but it is not
clear if this theoretical prediction holds when considering omnivorous species
(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
can generate the same pattern [@thibaut_understanding_2013].
Another explanation is that the fishes at higher trophic levels are not more
stable themselves, but rather allow for stronger top-down control and resource
complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
networks complicate the interpretation from the network to population
perspective. Over its life span, a given fish will change of diet and thus move
upward in the trophic chain. The dynamic of a given species composed
of several trophic species can thus be a mix of the dynamics of several trophic
levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
@medvinsky_modelling_2015]. Then, there is a clear need for a better
understanding of how the dynamics of pure food chain models would be affected by
inclusion of omnivory and ontogeny.

We found that connectance had no effect on temporal stability. This result
contradicts precedent theoretical studies on the relationship between stability
and network structure [@angelis_stability_1975; @may_will_1972;
@thebault_stability_2010], although they considered different stability concepts
and metrics [@arnoldi_resilience_2016]. Once again, it is possible that
that connectance from our networks contains too few information. Furthermore, a
crucial missing ingredient to go further is the interaction strength. Indeed,
@may_will_1972 has demonstrated theoretically the fundamental interplay between
connectance, species richness and average interaction strength
[@angelis_stability_1975; @dunne_network_2006].An alternative explanation can be
that connectance increases inhomogeneously in the food web, for instance a
higher connectance in lower trophic levels will not have the stabilising effects
conferred by higher predation and omnivory in higher trophic levels. Further
investigations on this effect is needed.

@@

We found that species richness had a positive and a negative effect on
respectively total biomass and its temporal stability whereas average trophic
level had a positive effect on both. It confirms that more investigation is
needed to understand the mechanisms leading to common and opposite effects of
horizontal and vertical diversity. We found that connectance covaries
negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
@thebault_stability_2010], connectance had itself no effects on both total
biomass and its temporal stability. On the other side, we found species richness
was negatively related to mean trophic level and mean trophic level
covariated positively with total biomass and its temporal stability. Hence,
horizontal diversity had a direct positive and negative effect respectively on
total biomass and its stability but a negative and positive effect through
vertical diversity.  Theoretical work have shown that species richness can be
linked to allocation of biomass toward higher trophic level
[@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
It indicates the importance to consider both horizontal, vertical diversity and
their dependence. Moreover, it calls for further investigations on how species
diversity variation translates in network structure.

@thibaut_understanding_2013 have theoretically shown that a highly positive
relationship between species variance and mean together with a positive
relationship between mean species abundance (i.e. dominance) and species
richness should drive to a negative temporal stability-species richness
relationship. @thebault_relationship_2006 have also shown in a bi-trophic
foodweb that a negative temporal stability-species richness appears in case of a
plant species is highly dominant through low consumption by consumers but in the
same time highly variable because of low competitive ability. Then, common
mechanisms might be at play for both horizontal and vertical diversity while
having same or opposite effects on total biomass and its temporal stability.
Overall our results confirm that more investigation is needed to understand the
mechanisms leading to common and opposite effects of horizontal and vertical
diversity.

In
trophic communities,  additionnaly to the **portefolio effect**, the importance
of trophic interactions on synchrony (mal dit).

@@

We find that environmental drivers overall affect total biomass indirectly,
through changes in vertical and horizontal diversity. This contrasts with
research in plant communities that showed that total biomass was primarily
driven by environmental factors [@grace_integrative_2016], and in particular by
warming, which has contrasted effects on biomass in aquatic communities
[@yvondurocher_warming_2011; @dossena_warming_2012]. Average temperature,
inverse altitude, and average stream size had indirect positive effects on total
biomass, through a positive direct effect on species richness. These effects are
well known in freshwater communities and are explained by a gain in species
along thermal gradients, from smaller and colder streams, which support small
food webs dominated by salmonids [@ogorman_chapter_2012; @emmrich_geographical_2014],
to wider and warmer sections of river networks, which contain larger food webs
dominated by mesotrophic preators such as percids [@allan_stream_2007;
@emmrich_geographical_2014]. Further in line with this pattern, we find that average stream
size had a positive effect on total biomass through
a positive effect on mean trophic level, consistent with the fact that food
webs in wider streams, with a greater amount of running waters, are also larger,
and hence support more species and biomass [@allan_stream_2007]. Greater ecosystem
size might be linked to a greater diversity of resources through habitat
heterogeneity, on so higher species richness and total biomass by surface unit,
through resource complementarity. Greater diversity of resources might also
allow to maintain higher biomass in high trophic level [@post_ecosystem_2000;
@doi_resource_2009]. Overall, our results indicate that environmental effects on
total biomass operate primarily through changes in community structure.
Furthermore, the positive effect of temperature on total biomass was of the
magnitude of effects of horizontal and vertical diversity, and thereby of
changes in community structure. This adds to the mounting body of work reporting
important effects of temperature on the structure and biomass of aquatic system
[e.g. @dossena_warming_2012; @edeline_ecological_2013;
@emmrich_geographical_2014; @hattab_forecasting_2016].

Interestingly, stream flow and size, inverse altitude, and temperature had
indirect effects on stability through two conflicting pathways, either
stabilising, involving vertical diversity, or destabilising, involving
horizontal diversity. The first pathway consists in a positive effect of
temperature and stream properties on mean trophic level, in line with the idea
that wider streams and warmer conditions are favourable to mesotrophic predators
[@allan_stream_2007; @emmrich_geographical_2014], which in turn stabilises
biomass fluctuations, possibly due to increased top-down regulation (as
discussed above). The second pathway consists in a positive effect of
temperature and stream properties (width, flow, inverse altitude) on species
richness, which itself has a destabilising effect (see discussion on horizontal
diversity). This result is interesting in that though both pathways had not been
evidenced to be at jointly play, as far as we know. Furthermore, it is unclear
as to which pathway is dominating, and under which circumstance, opening an
interesting avenue for further investigations. Overall our study highlights
that environmental factors should not be ignored in natural communities studies
and that its effects can be mainly indirect and in this case, path analysis
should more relevant than bivariate relationships
[@grace_causal_2014; @grace_integrative_2016].

@@

We aimed to assess the effect of horizontal & vertical diversity on empirical
trophic communities. While theoretical ecology has focused on the effects of
network structure on stability, empirical ecology has focused on species richness
and ignored network structure. Furthermore, both fields have largely used
different stability metrics. We showed that horizontal and vertical diversity
can have independent and sometimes opposite effects on total biomass and its
temporal stability. It opens a promising way for the understanding on how
species interactions, of different types, can affect both synchrony and CVsp in
different ecosystems. The reconstruction of ecological networks based on trait
can be a first approach to document such relationships, however it will not
compensate for close evaluation of measured interaction strength. We also
believe that SEM methods are particularly helpful to assess complex relationship
between environment, community structure and ecosystem properties in empirical
data which necessitate to move from simple bivariate relationships
[@grace_integrative_2016]. We believe that the integration of network structure
and species interaction will improve our understanding of the mechanisms driving
ecosystem properties.

>>>>

Our aim was to evaluate the effects of the network structure on the total
biomass and its temporal stability in natural communities, which have been
poorly documented. To do so, we quantified the effects, directs and indirects,
of habitat properties, species richness, and food web structure, on the biomass
and stability of fish communities, from the ONEMA fish dataset, containing over
X million individual fish samples, across 99 locations in France from 1995 to
2018. We infered trophic interactions networks based on body size-dependency in
   food diet from the literature and prey/predator body size
ratio for piscivory^[ We inferred trophic networks at the scale of trophic
species (i.e. nodes being body size classes) to take in account ontogenic diet
shifts and that fish-fish trophic interaction depends on body size ratio between
prey and predator. On the other side, the community metrics were defined at the
species level, (i.e.  species richness, average species CV and synchrony).  ].
We built structural equation models to disantangle the direct and indirect
effects of environmental drivers, species richness and network structure on both
total biomass and biomass stability.  We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively.  Futhermore, we found that the effect of species richness
and mean trophic level on total biomass and its temporal stability were not
independant as species richness had a positive effect on mean trophic level.
Finally, we found that the magnitude of the effects of average temperature and
altitude was equal or superior to the effects of species richness and mean
trophic level. Overall, our study is unique by its level of integration, from
environmental effects to total biomass and stability, going through species
richness and network structure, and the first direct assessment of a possible
joint effect of species richness and network structure.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
richness on total biomass might be due to resource use complementarity, which is
held by niche differentiation and interspecific facilitation
[@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
or might be due to a positive selection effect [@tilman_plant_1997;
@loreau_partitioning_2001], which leads to the dominance of the most productive
species. Previous research seems to indicate that resource complementarity might
be the main driver in fish communities [@carey_determining_2011].

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in grasslands
[@tilman_biodiversity_2006]; mesocosms (Pennekamp et al. 2018), in 
butterflies natural communities [@olivier_independent_nodate] or even in lotic
fish communities [@franssen_annual_2011] where positive relationships were found
between temporal stability and species richness. However other studies found a
opposite relationship in natural grassland [@yang_effects_2011] or a marginal
one in natural forests [@declerck_species_2006]. A first step to identify the
mechanisms behind those contrasting patterns is be to look at the effects of
species richness on synchrony and $\overline{CV_{sp}}$, which constitute the two
components of temporal stability quantified as CV [@loreau_species_2008;
@thibaut_understanding_2013].

We found that species richness decreases
synchrony, thereby increasing stability. Species richness can reduce synchrony
by decreasing of population size, thus raising the role of demographic
stochasticity on population dynamics [@loreau_species_2008] but also in the case
where species have different responses to environmental variation
[@loreau_species_2008]. While a negative effect of species richness on synchrony
is generally found in experimental grasslands [@isbell_biodiversity_2009;
@roscher_identifying_2011], no relation has been found in natural forests
[@declerck_species_2006], but negative relationships have been found in natural
communities of birds, bats, grasslands, bats and butterflies
[@bluthgen_land_2016; @olivier_independent_nodate]. Our study thus highlights
that species richness might also decrease synchrony in empirical trophic
communities. The positive effect of species richness on $\overline{CV_{sp}}$,
thereby decreasing stability, is more intriguing. While  positive effect of
species richness on $\overline{CV_{sp}}$ was reported in experimental grasslands
and natural bird communities [@tilman_biodiversity_2006;
@olivier_independent_nodate], negative and neutral relationships have been found
in butterfly and bat communities. @thibaut_understanding_2013 proposed that a
strongly uneven biomass distribution across population and that the biomass
variance of population increases much faster than its mean can generate a
positive effect of species richness on population ($\overline{CV_{sp}}$)
stability. It was unexpected that the average population $\overline{CV_{sp}}$ had
a stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_independent_nodate], and explain why we observe a
negative effect of species on temporal stability of biomass. The lower
effect of synchrony can be explained by the the presence of generalist predator
in stream communities, which can raise synchrony between prey species which
shares the same predator [@raimondo_interspecific_2004]. Alternatively,
uneveness can also raise synchrony between species
[@thibaut_understanding_2013], in line with mecanisms which can raise positive
relationships between $\overline{CV_{sp}}$ and species richness.

@@

The mean trophic level was positively linked to total biomass. This result is
straightforward. As feeding interactions were partly determined by body size and
that body mass increase with body size, it is expected that the more the average
biomass is located at higher trophic level, the more the total biomass
increase. A mechanism, suggested by experimental and theoretical work, can
be that a higher trophic level is the result of a stronger top-down effect,
meaning higher predation rates and biomass fluxes to higher trophic levels
[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
increase in total biomass with trophic length. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increases
with the length of trophic chain and so results in higher total biomass. 
In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance should translate in higher resource transfer
efficiency between prey and predators and so results in higher total biomass in
the fish compartment. A reason for such an absence of an effect might be due the
absence of information that we have about the other compartments of the
community, i.e, the primary producers, zooplankton and zoobenthos. Further
research are needed to assess the role of the trophic structure with a more
complete communities.

Mean trophic level had a positive effect on biomass stability by its negative
effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
means that species at higher trophic level are more stable than the species at
lower trophic levels. Strong top-down control can generate this pattern in pure
trophic chain [@barbier_pyramids_2018; @shanafelt_stability_2018] but it is not
clear if this theoretical prediction holds when considering omnivorous species
[@wang_biodiversity_2016] and if other mechanisms can generate the same pattern
[@thibaut_understanding_2013]. Another explanation is that the fishes at higher
trophic levels are not more stable themselves, but rather allow for stronger
top-down control and resource complementarity and thus reduce biomass
fluctuations in lower trophic levels [@rooney_structural_2006;
@neutel_reconciling_2007]. However, the ontogenic nature of the trophic networks
complicate the interpretation from the network perspective to population
fluctuations, the network structure fluctuate according to change in population
size structure. Generally, a fish will change of diet over its life span and
thus move upward in the trophic chain. The temporal dynamic of a given species
composed of several trophic species can thus be a mix of the dynamics of several
trophic levels, plus the oscillatory dynamics of the cohorts
[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
need for a better understanding of how the dynamics of pure food chain models
would be affected by inclusion of omnivory and ontogeny. We found that
connectance had no effect on temporal stability. This result previous precedent
theoretical studies on the relationship between stability and network structure
[@angelis_stability_1975; @may_will_1972; @thebault_stability_2010], although
they considered different stability concepts and metrics
[@arnoldi_resilience_2016]. Once again, it is possible that that connectance
from our networks contains too few information. Furthermore, a crucial missing
ingredient to go further is the interaction strength. Indeed, interaction
strength is a crucial ingredient of stability [@may_will_1972;
@angelis_stability_1975; @dunne_network_2006]. An alternative explanation can be
that connectance increases inhomogeneously in the food web, for instance a
higher connectance in lower trophic levels will not have the stabilising effects
conferred by higher predation and omnivory in higher trophic levels. Further
investigations on this effect is needed.

@@

We found that species richness had a positive and a negative effect on
respectively total biomass and its temporal stability whereas average trophic
level had a positive effect on both. It confirms that more investigation is
needed to understand the mechanisms leading to common and opposite effects of
species richness and network structure. We found that connectance covaries
negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
@thebault_stability_2010], connectance had itself no effects on both total
biomass and its temporal stability. On the other side, we found that species richness
was negatively related to mean trophic level and mean trophic level
covariated positively with total biomass and its temporal stability. Hence,
species richness had a direct positive and negative effect respectively on
total biomass and its stability but a negative and positive effect through
mean trophic level. Theoretical work have shown that species richness can be
linked to allocation of biomass toward higher trophic level
[@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
It indicates the importance to consider both species richness, network structure
and their dependence. It calls for further investigations on how species
diversity variation translates in network structure. Finally, common mechanisms
might be at play in mono and multi-trophic communities such as while having same or
opposite effects on total biomass and its temporal stability.

@@

We find that environmental drivers overall affect total biomass indirectly,
through changes in network structure and species richness. This contrasts with
research in plant communities that showed that total biomass was directly driven
by environmental factors [@grace_integrative_2016], and in particular by
warming, which has contrasted effects on biomass in aquatic communities
[@yvondurocher_warming_2011; @dossena_warming_2012]. Average temperature,
inverse altitude, and average stream size had indirect positive effects on total
biomass, through a positive direct effect on species richness. These effects are
well known in biogeography and in freshwater communities and are explained by a gain in species
along thermal gradients, from smaller and colder streams, which support small
food webs dominated by salmonids [@ogorman_chapter_2012;
@emmrich_geographical_2014], to wider and warmer sections of stream networks,
which contain larger food webs dominated by mesotrophic preators such as percids
[@allan_stream_2007; @emmrich_geographical_2014]. Further in line with this
pattern, we find that average stream size had a positive effect on total biomass
through a positive effect on mean trophic level, consistent with the fact that
food webs in wider streams, with a greater amount of running waters, are also
larger, and hence support more species and biomass [@allan_stream_2007]. Greater
ecosystem size might be linked to a greater diversity of resources through
habitat heterogeneity, on so higher species richness and total biomass by
surface unit, through resource complementarity. Greater diversity of resources
might also allow to maintain higher biomass in high trophic level
[@post_ecosystem_2000; @doi_resource_2009]. Overall, our results indicate that
environmental effects on total biomass operate primarily through changes in
community structure. Furthermore, the positive effect of temperature on total
biomass was of the magnitude of effects of network structure and species
richness. This adds to the mounting body of work reporting important effects of
temperature on the structure and biomass of aquatic system [e.g.
@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
@hattab_forecasting_2016].

Interestingly, stream flow and size, inverse altitude, and temperature had
indirect effects on stability through two conflicting pathways, either
stabilising, involving network structure, or destabilising, involving
species richness. The first pathway consists in a positive effect of
temperature and stream properties on mean trophic level, in line with the idea
that wider streams and warmer conditions are favourable to mesotrophic predators
[@allan_stream_2007; @emmrich_geographical_2014], which in turn stabilises
biomass fluctuations, possibly due to increased top-down regulation (as
discussed above). The second pathway consists in a positive effect of
temperature and stream properties (width, flow, inverse altitude) on species
richness, which itself has a destabilising effect (see discussion on species).
This result is interesting in that though both pathways had not been evidenced
to be jointly to play, as far as we know. Furthermore, it is unclear
as to which pathway is dominating, and under which circumstance, opening an
interesting avenue for further investigations. Overall our study highlights
that environmental factors should not be ignored in natural communities studies
and that its effects can be mainly indirect and in this case, path analysis
should more relevant than bivariate relationships
[@grace_causal_2014; @grace_integrative_2016].

@@

We aimed to assess the effect of species richness & network structure on empirical
trophic communities. While theoretical ecology has focused on the effects of
network structure on stability, empirical ecology has focused on species richness
and ignored network structure. Furthermore, both fields have largely used
different stability metrics. We showed that species richness and network
structure can have independent and sometimes opposite effects on total biomass
and its temporal stability. It opens a promising way for the understanding on
how species interactions, of different types, can affect both synchrony and $\overline{CV_{sp}}$
in different ecosystems. However, the mecanisms leading to such patterns remains
to be elucidated. The reconstruction of ecological networks based on body size
and food diet litterarure can be a first approach to document such
relationships, however it will not compensate for close evaluation of measured
interaction strength. We also believe that SEM methods are particularly helpful
to assess complex relationship between environment, community structure and
ecosystem properties in empirical data which necessitate to move from simple
bivariate relationships [@grace_integrative_2016]. We believe that the
integration of network structure and species interaction will improve our
understanding of the mechanisms driving ecosystem properties.
